A seamless, client-centric programming model for type safe web applications

### 2014-05-02 paper.tex
Add Ocsigen to related work.

@@

>>>>

\paragraph{Ocsigen} Ocsigen\ \cite{ocsigen} enables the development of
client-server web applications using O'Caml. It accomplishes typed, seamless
communication by exposing mutable variables across the network. While this is a
quite flexible programming model, we believe that this uncontrolled, implicit
information flow makes programs harder to follow, debug, secure and optimize.

@@

\bibitem[Balat (2006)]{ocsigen}
V. Balat. "Ocsigen: typing web interaction with objective Caml." Proceedings of the 2006 workshop on ML. ACM, 2006.
